Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-08-24 icse/paper.tex
Ana

\acmConference[ICSE 2020]{Technical Papers}{May 23--29}{Seoul, South Korea}

@@

\author{Simon Baars}
\affiliation{\institution{University of Amsterdam}}
\email{simon.mailadres@gmail.com}

\author{Ana Oprescu}
\affiliation{\institution{University of Amsterdam}}
\email{a.m.oprescu@uva.nl}

@@

We address this shortcoming by first analyzing what data should be gathered from an automatically refactored system. We then propose a tool to detect clones, analyze their context and automatically refactor a subset of them. We use a set of established metrics to determine the impact of the applied refactorings on the maintainability of the system. Based on these results, one could decide which clones improve system design when refactored. We evaluate our approach over a large corpus of open source Java projects.

@@

\section{Related Work}
The state-of-the-art in code clone refactoring is the work by Mazinanian et al.~\cite{mazinanian2016jdeodorant}. The authors propose a tool named JDeodorant that can automatically refactor a subset of duplication problems. This tool is based on several studies that look into different aspects of code clone refactoring. In a study by Krishnan et al.~\cite{krishnan2013refactoring} clone refactoring is approached as an optimization problem: how does variability between cloned fragments influence the refactoring techniques required and their implications on system design. Another study by Krishnan et al.~\cite{krishnan2014unification} proposes a list of preconditions for clones to determine their refactorability. This list is revised by Tsantalis et al.~\cite{tsantalis2015assessing}, proposing a set of 8 preconditions that determine whether two duplicated fragments can be refactored. In a recent study, Tsantalis et al.~\cite{tsantalis2017clone} look into how lambda's can provide help in the clone refactoring process.

In their work, the main focus is to find out which clones \textbf{can} be refactored. We extend this work by looking into which clones \textbf{should} be refactored. We propose definitions for refactorable clones together with thresholds to be able to limit their negative impact on system design. We measure which clones improve maintainability when refactored. This results in a set of thresholds that can be used to detect and refactor clones that should be refactored.

@@

To detect clones that can be automatically refactored, we propose to:
\begin{itemize}
  \item Compare variable references not only by their name but also by their type.
  \item Compare referenced types by their fully qualified identifier (FQI). The FQI of a type reference describes the full path to where it is declared.
  \item Compare method references by their fully qualified signature (FQS). The FQS of a method reference describes the full path to where it is declared, plus the FQI of each of its parameters.
\end{itemize}

>>>>

\acmConference[ICSE 2020]{Technical Papers}{}{}

@@

%\author{Simon Baars}
%\affiliation{\institution{University of Amsterdam}}
%\email{simon.mailadres@gmail.com}

%\author{Ana Oprescu}
%\affiliation{\institution{University of Amsterdam}}
%\email{a.m.oprescu@uva.nl}

@@

We address this shortcoming by first analyzing what data should be gathered from an automatically refactored system. We then propose a tool to detect clones, analyze their context and automatically refactor a subset of them. We use a set of established metrics to determine the impact of the applied refactorings on the maintainability of the system. Based on these results, one could decide which clones would improve system design if refactored. We evaluate our approach over a large corpus of open source Java projects.

@@

\section{Related Work}
The state-of-the-art in code clone refactoring is the work by Mazinanian et al.~\cite{mazinanian2016jdeodorant}. The authors propose a tool named JDeodorant that can automatically refactor a subset of duplication problems. This tool is based on several studies that look into different aspects of code clone refactoring. In a study by Krishnan et al.~\cite{krishnan2013refactoring} clone refactoring is approached as an optimization problem: how does variability between cloned fragments influence the refactoring techniques required and their implications on system design. Another study by Krishnan et al.~\cite{krishnan2014unification} proposes a list of preconditions for clones to determine their refactorability. This list is revised by Tsantalis et al.~\cite{tsantalis2015assessing}, proposing a set of 8 preconditions that determine whether two duplicated fragments can be refactored.

A recent study~\cite{tsantalis2017clone} looks into how lambdas can assist the clone refactoring process. The main focus is to find out which clones \textbf{can} be refactored. We extend this work by looking into which clones \textbf{should} be refactored. We propose definitions for refactorable clones together with thresholds to be able to limit their negative impact on system design. We measure which clones improve maintainability when refactored. This results in a set of thresholds that can be used to detect and refactor clones that should be refactored.

@@

To detect automatically refactorable clones, we propose to:
\begin{itemize}
  \item Compare variable references not only by their name but also by their type.
  \item Compare referenced types by their fully qualified identifier (FQI). The FQI of a type reference describes the full path to where it is declared.
  \item Compare method references by their fully qualified signature (FQS). The FQS of a method reference describes the full path to where it is declared, plus the FQI of each of its parameters.
\end{itemize}
